Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

## Poin 3

@@

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(norm_means, main = "Normal QQ Plot", col = "#8DC16D", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means, col = "red", lwd=2)

qqnorm(unif_means, main = "Uniform QQ Plot", col = "#4493CA", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(unif_means, col = "red", lwd=2)

qqnorm(exp_means, main = "Exponensial QQ Plot", col = "#D44155", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(exp_means, col = "red", lwd=2)
```

>>>>

## Poin 3 {.tabset}

@@

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(norm_means[[1]], main = "QQ-Plot Normal", col = "#8DC16D", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means[[1]], col = "red", lwd=2)

qqnorm(norm_means[[2]], main = "QQ-Plot Normal", col = "#8DC16D", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means[[2]], col = "red", lwd=2)

qqnorm(norm_means[[3]], main = "QQ-Plot Normal", col = "#8DC16D", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(norm_means[[3]], col = "red", lwd=2)
```

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(unif_means[[1]], main = "QQ-Plot Seragam", col = "#4493CA", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(unif_means[[1]], col = "red", lwd=2)

qqnorm(unif_means[[2]], main = "QQ-Plot Seragam", col = "#4493CA", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(unif_means[[2]], col = "red", lwd=2)

qqnorm(unif_means[[3]], main = "QQ-Plot Seragam", col = "#4493CA", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(unif_means[[3]], col = "red", lwd=2)
```

```{r fig.height=3.5, fig.width=10, dpi=300}
par(mfrow = c(1, 3))
qqnorm(exp_means[[1]], main = "QQ-Plot Eksponensial\nUkuran Sample (n=2)", col = "#D44155", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(exp_means[[1]], col = "red", lwd=2)

qqnorm(exp_means[[2]], main = "QQ-Plot Eksponensial\nUkuran Sample (n=5)", col = "#D44155", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(exp_means[[2]], col = "red", lwd=2)

qqnorm(exp_means[[3]], main = "QQ-Plot Eksponensial\nUkuran Sample (n=25)", col = "#D44155", lwd = 7,
       xlab = "Theoretical Quantiles", ylab = "Sample Quantiles")
qqline(exp_means[[3]], col = "red", lwd=2)
```
